%# -*- coding: utf-8-unix -*-
%%==================================================
%% pub.tex for SJTUThesis
%% Encoding: UTF-8
%%==================================================

\begin{publications}{99}
 \item {\bf Zhehuai Chen}, Jasha Droppo, Jinyu Li, Wayne Xiong, Progressive Joint Modeling in Unsupervised Single-channel Overlapped Speech Recognition. IEEE/ACM Transactions on Audio, Speech, and Language Processing, vol. 26, no. 1, pp. 184-196, Jan. 2018. doi:  10.1109/TASLP.2017.2765834.
 \item {\bf Zhehuai Chen}, Yimeng Zhuang, Yanmin Qian, Kai Yu. Phone Synchronous Speech Recognition with CTC Lattices. IEEE/ACM Transactions on Audio, Speech and Language Processing, vol. 25, no. 1, pp. 86-97, Jan. 2017. doi: 10.1109/TASLP.2016.2625459.
  \item {\bf Zhehuai Chen}, Yanmin Qian, Kai Yu, Sequence Discriminative Training for Deep Learning based Acoustic Keyword Spotting. Speech Communication, vol. 102, 100-111, 2018.
 \\
    \item {\bf Zhehuai Chen}, Justin Luitjens, Hainan Xu, Yiming Wang, Daniel Povey, Sanjeev Khudanpur, A GPU-based WFST Decoder with Exact Lattice Generation,  19th Annual Conference of  International Speech Communication Association (InterSpeech), 2018 {\bf [Best Paper Nomination]}.
  \item {\bf Zhehuai Chen}, Linguistic Search Optimization for Deep Learning Based LVCSR, in Doctoral Consortium, 19th Annual Conference of  International Speech Communication Association (InterSpeech), 2018.
  \item {\bf Zhehuai Chen}, Jasha Droppo, Sequence Modeling in Unsupervised Single-channel Overlapped Speech Recognition,  IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), Calgary, Canada, 2018.
  \item {\bf Zhehuai Chen}, Qi Liu, Hao Li, Kai Yu, On Modular Training of Neural Acoustics-to-word Model for LVCSR,  IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), Calgary, Canada, 2018.
 \item {\bf Zhehuai Chen}, Yanmin Qian, and Kai Yu. A unified confidence measure framework using auxiliary normalization graph, IScIDE, 2017.
 \item {\bf Zhehuai Chen}, Yimeng Zhuang, Kai Yu. Confidence Measures for CTC-based Phone Synchronous Decoding. IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), New Orleans, USA, 2017.
 \item {\bf Zhehuai Chen}, Wei Deng, Tao Xu, Kai Yu. Phone Synchronous Decoding with CTC Lattice. 17th Annual Conference of the International Speech Communication Association (InterSpeech), San Francisco, America, 2016.
 \item {\bf Zhehuai Chen}, Kai Yu, An Investigation of Implementation and Performance Analysis of DNN Based Speech Synthesis System. 12th IEEE International Conference on Signal Processing (ICSP), Hangzhou, 2014.
 \\
 \item {\bf 陈哲怀}, 郑文露, 游永彬, 钱彦旻, 俞凯, 标签同步解码算法及其在语音识别中的应用. 计算机学报 (投出) , 2019.
 \\
 \item Mingkun Huang, Yongbin You, {\bf Zhehuai Chen}, Yanmin Qian, Kai Yu. Knowledge Distillation for Sequence Model, 19th Annual Conference of  International Speech Communication Association (InterSpeech), 2018.
 \item Yue Wu, Tianxing He, {\bf Zhehuai Chen}, Yanmin Qian and Kai Yu. Multi-view LSTM Language Model with Word-synchronized Auxiliary Feature for LVCSR, CCL, 2017.
 \item Da Zheng, {\bf Zhehuai Chen}, Yue Wu, Kai Yu, Directed Automatic Speech Transcription Error Correction Using Bidirectional LSTM. International Symposium on Chinese Spoken Language Processing (ISCSLP), Tianjin, China, 2016.
 \item Bo Chen, {\bf Zhehuai Chen}, Jiachen Xu, Kai Yu. An Investigation of Context Clustering for Statistical Speech Synthesis with Deep Neural Network. 16th Annual Conference of the International Speech Communication Association (InterSpeech), Dresden, Germany, 2015.
\end{publications}
