%# -*- coding: utf-8-unix -*-
%%==================================================
%% pub.tex for SJTUThesis
%% Encoding: UTF-8
%%==================================================

\begin{publications}{99}
 \item {\bf 第一作者}, Progressive Joint Modeling in Unsupervised Single-channel Overlapped Speech Recognition. IEEE/ACM Transactions on Audio, Speech, and Language Processing, vol. 26, no. 1, pp. 184-196, Jan. 2018. doi:  10.1109/TASLP.2017.2765834.
 \item {\bf 第一作者}, Phone Synchronous Speech Recognition with CTC Lattices. IEEE/ACM Transactions on Audio, Speech and Language Processing, vol. 25, no. 1, pp. 86-97, Jan. 2017. doi: 10.1109/TASLP.2016.2625459.
  \item {\bf 第一作者}, Sequence Discriminative Training for Deep Learning based Acoustic Keyword Spotting. Speech Communication, vol. 102, 100-111, 2018.
  \item {\bf 第一作者}, 标签同步解码算法及其在语音识别中的应用[J]. 计算机学报, 2019.
 \\
  \item {\bf 第一作者}, Mahaveer Jain, Yongqiang Wang, Michael Seltzer, Christian Fuegen, End-to-end Contextual Spebech Recognition using Class Language Models and a Token Passing Decoder, IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), Brighton, UK, 2019.
  \item {\bf 第一作者}, A GPU-based WFST Decoder with Exact Lattice Generation,  19th Annual Conference of  International Speech Communication Association (InterSpeech), 2018 {\bf [Best Paper Nomination]}.
  \item {\bf 第一作者}, Linguistic Search Optimization for Deep Learning Based LVCSR, in Doctoral Consortium, 19th Annual Conference of  International Speech Communication Association (InterSpeech), 2018.
  \item {\bf 第一作者}, Sequence Modeling in Unsupervised Single-channel Overlapped Speech Recognition,  IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), Calgary, Canada, 2018.
  \item {\bf 第一作者}, On Modular Training of Neural Acoustics-to-word Model for LVCSR,  IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), Calgary, Canada, 2018.
 \item {\bf 第一作者}, A unified confidence measure framework using auxiliary normalization graph, IScIDE, 2017.
 \item {\bf 第一作者}, Confidence Measures for CTC-based Phone Synchronous Decoding. IEEE International Conference on Acoustics, Speech and Signal Processing (ICASSP), New Orleans, USA, 2017.
 \item {\bf 第一作者}, Phone Synchronous Decoding with CTC Lattice. 17th Annual Conference of the International Speech Communication Association (InterSpeech), San Francisco, America, 2016.
 \item {\bf 第一作者}, An Investigation of Implementation and Performance Analysis of DNN Based Speech Synthesis System. 12th IEEE International Conference on Signal Processing (ICSP), Hangzhou, 2014.
 \\
 \item 第三作者, Knowledge Distillation for Sequence Model, 19th Annual Conference of  International Speech Communication Association (InterSpeech), 2018.
 \item 第三作者, Multi-view LSTM Language Model with Word-synchronized Auxiliary Feature for LVCSR, CCL, 2017.
 \item 第二作者, Directed Automatic Speech Transcription Error Correction Using Bidirectional LSTM. International Symposium on Chinese Spoken Language Processing (ISCSLP), Tianjin, China, 2016.
 \item 第二作者, An Investigation of Context Clustering for Statistical Speech Synthesis with Deep Neural Network. 16th Annual Conference of the International Speech Communication Association (InterSpeech), Dresden, Germany, 2015.
\end{publications}
